Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-04 contents/draft.tex
Update abstract!

    \abstract[Abstract]{
        This study presents a novel approach to Korean morphological analysis by integrating a Transformer-based re-ranking method into a dictionary-based morphological analysis system.
        A significant advancement in this research is the effective utilization of the BERT model's re-ranking, which has brought innovations in the broader field of natural language processing.
        This enhancement is achieved through a two-stage re-ranking process: the first stage involves fine-tuning a BERT model using only the results of morphological analysis, and the second stage fine-tunes a different type of BERT model using the re-ranked results along with the original text.
        This method effectively improves the performance of dictionary-based morphological analysis, which previously lagged behind syllable-based analysis in terms of accuracy.
        The integration of deep learning with traditional morphological analysis represents a significant advancement in providing more powerful and efficient tools for language processing tasks.
        According to our results, there is a substantial improvement in eojeol accuracy and morpheme F1 scores compared to previous methods.
        This study not only sets a new standard in Korean language processing but also paves the way for further advancements in applying deep learning to linguistic analysis.
    }
    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}

>>>>

    \abstract[Abstract]{
        This study introduces a novel approach in Korean morphological analysis, merging dictionary-based techniques with Transformer-based deep learning models.
        A significant aspect of this research is the use of a BERT-based re-ranking system, which substantially enhances the accuracy of dictionary-based morphological analysis.
        The methodology involves generating multiple suboptimal paths for morphological analysis and then employing BERT models for their re-ranking, capitalizing on their advanced language context comprehension.

        The results showcase a remarkable enhancement in morphological analysis performance, with the first-stage re-ranking achieving over a 20\% improvement in ERR compared to existing models.
        The second-stage re-ranking, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
        These figures indicate a significant stride forward in accuracy, demonstrating the efficacy of combining traditional dictionary-based analysis with contemporary deep learning techniques.

        This study paves the way for future advancements in Korean language processing.
        It suggests exploring more refined integrations of dictionary and deep learning approaches and utilizing probabilistic models to further enhance morphological analysis.
        The success of this hybrid approach sets a new benchmark in the field and offers valuable insights for tackling similar challenges in other language processing applications.
    }
    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}
